---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: inline
---
```{r pkg-knitr-opts, include=FALSE}
knitr::opts_chunk$set(collapse=TRUE, fig.retina=2, message=FALSE, warning=FALSE)
options(width=120)
```

[![Travis-CI Build Status](https://travis-ci.org/hrbrmstr/securitytrails.svg?branch=master)](https://travis-ci.org/hrbrmstr/securitytrails) 
[![Coverage Status](https://codecov.io/gh/hrbrmstr/securitytrails/branch/master/graph/badge.svg)](https://codecov.io/gh/hrbrmstr/securitytrails)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/securitytrails)](https://cran.r-project.org/package=securitytrails)

# securitytrails

Tools to Query the '[SecurityTrails](https://securitytrails.com/corp/api)' 'API'

## Description

'[SecurityTrails](https://securitytrails.com/corp/api)' (<securitytrails.com>) offers an 'API' to query information about domains, 'IP' addresses, hostnames and more. Methods are provided to query 'SecurityTrails' 'API' endpoints.

## What's Inside The Tin

- `st_assoc_domains`:	Find associated domains
- `st_dns_history`:	DNS history by record type
- `st_domain`:	Get Domain
- `st_domain_search`:	Search Domain (Filter strings)
- `st_explore_ips`:	Explore IPs
- `st_ping`:	Test Access To the SecurityTrails API
- `st_subdomains`:	List Subdomains
- `st_tags`:	List Tags
- `st_whois`:	Get WHOIS
- `st_whois_history`:	WHOIS history by domain
- `trails_api_key`:	Get or set `SECURITYTRAILS_API_KEY` value

The following functions are implemented:

## Installation

```{r install-ex, eval=FALSE}
devtools::install_git("https://gitlab.com/hrbrmstr/securitytrails.git")
# or
devtools::install_github("hrbrmstr/securitytrails")
```

## Usage

```{r lib-ex}
library(securitytrails)

# current version
packageVersion("securitytrails")

```

## securitytrails Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
